---
title: "Perception of Founders' Age in Startups"
author: "Dr Preet Deep Singh"
affiliation: "Invest India"
date: "08/09/2021"
output: 
  bookdown::pdf_document2:
    toc: no
    citation_package: natbib
    number_sections: yes
    keep_tex: yes
abstract: "I look at the perception of the age of startup founders. I find that founders in their early thirties are less likely to succeed and get funded and more likely to abandon. Females rated female founders aged 32,33 as consistently lower than 22,23-year-old female founders to succeed. Males in their early twenties were more likely to abandon their startup than females in their early forties. This points to a stronger perceived bias within females than with the general population which could have social reasons. Male respondents felt that 32,33 year old male founders were more likely to abandon their startup as compared to 32,33-year-old females. This research suggests specific steps for founders while pitching to customers/buyers. "
documentclass: "article"
editor_options: 
  chunk_output_type: console
bibliography: references.bib
link-citations: true
csl: apa.csl
---


```{r setup, echo=FALSE, , message=FALSE, tidy=TRUE}
library(dplyr)
library(stargazer)
library(lubridate)
library(formatR)
library(bookdown)

files<-list.files (pattern = "csv$")
#Load all files
FailedFounder<-read.csv("FailedFounder.csv")
Female12th<-read.csv("Female12th.csv")
FemaleFailedFounder<-read.csv("FemaleFailedFounder.csv")
FemaleIITIIM<-read.csv("FemaleIITIIM.csv")
FemaleMidAge<-read.csv("FemaleMidAge.csv")
FemaleOld<-read.csv("FemaleOld.csv")
FemaleYoung<-read.csv("FemaleYoung.csv")
GovtFather<-read.csv("GovtFather.csv")
Male12th<-read.csv("Male12th.csv")
MaleFailedFounder<-read.csv("MaleFailedFounder.csv")
MaleIITIIM<-read.csv("MaleIITIIM.csv")
MaleMidAge<-read.csv("MaleMidAge.csv")
MaleOld<-read.csv("MaleOld.csv")
MaleYoung<-read.csv("MaleYoung.csv")
SuccessfulEmployee<-read.csv("SuccessfulEmployee.csv")
SuccessfulFounder<-read.csv("SuccessfulFounder.csv")
#Rename ColumnNames
colnames(FailedFounder) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(Female12th) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(FemaleIITIIM) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(FemaleMidAge) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(FemaleOld) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(FemaleYoung) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(GovtFather) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(Male12th) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(MaleFailedFounder) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(FemaleFailedFounder) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(MaleIITIIM) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(MaleMidAge) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(MaleYoung) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(MaleOld) <-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(SuccessfulEmployee)<-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")
colnames(SuccessfulFounder)<-c("ResponseTime1","ResponseTime2","IP.Address","Age","Age.Range","Gender","Country","Success","Funding","Abandon")



FailedFounder$Name<-"FailedFounder"
SuccessfulEmployee$Name<-"SuccessfulEmployee"
SuccessfulFounder$Name<-"SuccessfulFounder"
FemaleFailedFounder$Name<-"FemaleFailedFounder"
MaleFailedFounder$Name<-"MaleFailedFounder"
GovtFather$Name<-"GovtFather"

MaleYoung$Name<-"MaleYoung"
FemaleYoung$Name<-"FemaleYoung"
FemaleMidAge$Name<-"FemaleMidAge"
MaleMidAge$Name<-"MaleMidAge"
MaleOld$Name<-"MaleOld"
FemaleOld$Name<-"FemaleOld"

Female12th$Name<-"Female12th"
Male12th$Name<-"Male12th"
MaleIITIIM$Name<-"MaleIITIIM"
FemaleIITIIM$Name<-"FemaleIITIIM"


mergedtest<-merge(GovtFather,FemaleFailedFounder, all.x=TRUE, all.y=TRUE) #This will work if there is a column with the name of the file. 
mergedtest<-merge(mergedtest,FailedFounder, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,SuccessfulEmployee, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,SuccessfulFounder, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,MaleFailedFounder, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,FemaleIITIIM, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,MaleIITIIM, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,Male12th, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,Female12th, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,FemaleYoung, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,FemaleMidAge, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,FemaleOld, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,MaleOld, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,MaleYoung, all.x=TRUE, all.y=TRUE)
mergedtest<-merge(mergedtest,MaleMidAge, all.x=TRUE, all.y=TRUE)

```

``` {r junk, echo=FALSE,  }

#*	 Education : DONE
#    *	Low Education
#    *	Technical Education
#    *	Management Education

#*	 Government Connect
#    *		 Family in government service
#    *		 Ex-government service

#*	 Age DONE
#	  *	 Young
#	  *	 Mid-age
#	  *	 Old

#*	 Region 
#	  *	 Metro city
#	  *	 Tier II City

#*	 Startup Experience
#	  *	 Founder
#		*	 Successful startup
#		*	 Failed startup
		
#*   Employee 
#		*	 Successful startup
#		*	 Failed startup

```

\section{Introduction}
TODO:1: Reread, sanitation
biblio-style: "apalike"

I take reference from @singh2021perception1, @singh2021perception3 and Look at the perception of  founder age measured by the probability of funding, probability of success and probability of abandonment of the startup. 
Younger males are more likely to succeed than MidAge females. Surprisingly females are driving this. It could be because 31,32 is the age for going the family way. This is evident in the fact that they rate 21,22 year old female founders as more likely to succeed, even more than YoungMale.

Consistently females have estimated the probability of funding for a startup founded by 31,32 year old females as much lower than that estimated by male respondents. Funding is a measure of how respondents feel investors would perceive the startup/founders. This means female respondents feel that investors would also not value 31,32 year old female founders, as opposed to male respondents. The estimate of female respondents for a startup founded by 21,22 year old females is higher than that of a startup founded by 31,32 year old females.

Male respondents felt that the probability of funding for a startup founded by young females was higher than that founded by older males. Surprisingly males also felt the probability of funding for a startup founded by 32,33 year old female founders was higher than that of a startup founded by 32,33 year old males. Their estimate for funding probability for older males was lower than that of 32,33 year old female founders also. On the contrary, female respondents felt that the probability of 42,43 year old males getting funded for their startup was higher than that of a startup founded by 32,33 year old females.

22,23 year old males were more likely to abandon their startup than 42,43 year old females. Males estimated that 32,33 year old females were more likely to abandon their startup as compared to 42,43 year old female founders who were also less likely than 22,23 year old males to abandon theirs. Surprisingly male respondents felt that 32,33 year old males were more likely than 32,33 year old females to abandon their startup. Perception is important because it leads to ABC \footnote{CITE LITERATURE HERE}.  #EDIT THIS

\section{Literature Review}
ADD CONTENT
		
\subsubsection{Age}
	While experience is considered as a major requirement in terms of employment, it may not be so for startups as we have seen success stories of college dropouts such as Bill Gates, Ritesh Agrawal, Steve Jobs and many other\footnote{FIND AN ARTICLE ABOUT THIS}. However, the spirit of entrepreneurship is not very strong in India. The education system therein does not lead to employability or maturity of the students as much as international curriculum. This is ingrained in people. Youth might be associated with recklessness and immaturity or inability to perceive risk\footnote{FIND REFERENCES}.
			
	We expect young startups to be perceived negatively. At 22,23, it is unlikely that the founders have had any relevant work experience. At 42, one might be perceived as more serious because one has a family and loans to take care of. Also, even if one started at a lower salary, over the course of two decades one might be earning more. If someone is willing to forego that amount, it would signal seriousness as the opportunity cost is much higher. We expect a similar effect on mid-age founder run startups but to a lesser extent.			
\section{Data and Method}
\subsection{Variables}
\subsubsection{Success}
  Success is not defined. The definition is kept open ended and it is based on perception of the participants.
\subsubsection{Funding}
  Hot stuff. News captures. How others/investors would perceive the founders and the startup.
\subsubsection{Abandonment}
  Associated with females that they might leave the startup due to societal pressure, matrimony or family needs.
\subsubsection{Age}
The founders across cases are aged 22,23 years (Case 1); 32,33 years (Case 2); and 42,43 years (Case 3). We 

\subsection{Method}
  We administered a survey to 300 participants. They were divided in six groups. Each group was given an identical case study of a startup and were asked to estimate the probability of success, probability of funding and probability of abandoning the startup. Each group had one of six cases as given below. 
\subsection{Data Summary}
Summary of the data and read out.
We name the cases as follows: 
Case 1a: Female founders, 20 named as FemaleYoung
Case 1b: Male founders, 20, named as MaleYoung

Case 2a: Female founders, 30, named as FemaleMidAge
Case 2b: Male founders, 30, named as MaleMidAge

Case 3a: Female founders, 40, named as FemaleOld
Case 3b: Male founders, 40, named as MaleOld

```{r datasummary1, echo=FALSE, message=FALSE,results='asis'} 

stargazer(select(FemaleYoung,-Age),title =  "This tables shows the summary of responses in the case where the startup founders were females aged 22 and 23 years.",label = "FemaleYoungsummary",header = FALSE) #This is because we will use Age Separately.
stargazer(select(FemaleMidAge,-Age),title = "This tables shows the summary of responses in the case where the startup founders were females aged 32 and 33 years." ,label = "FemaleMidAgesummary",header = FALSE)
stargazer(select(FemaleOld,-Age),title ="This tables shows the summary of responses in the case where the startup founders were females aged 42 and 43 years.",label = "FemaleOldsummary",header = FALSE)
stargazer(select(MaleYoung,-Age),title = "This tables shows the summary of responses in the case where the startup founders were males aged 22 and 23 years.",label = "MaleYoungummary",header = FALSE)
stargazer(select(MaleMidAge,-Age),title =  "This tables shows the summary of responses in the case where the startup founders were males aged 32 and 33 years.",label = "MaleMidAgesummary",header = FALSE) #This is because we will use Age Separately.
stargazer(select(MaleOld,-Age),title = "This tables shows the summary of responses in the case where the startup founders were males aged 42 and 43 years." ,label = "MaleOldsummary",header = FALSE)
#Add content on data, how many people, males or females, average of all three answers
##Total number, mean, max, min, 
```

\subsection{Results}
Graph on average results. This could be those box plots. 

\subsection{Success}
We look at the values for probability of success as estimated by our respondents across various age groups.

```{r success1, echo=FALSE,fig=TRUE, fig.width=7,fig.height=4, fig.cap="\\label{fig:boxsuccessage}This box plot shows the probablity of success as estimated across males and females and different age lvels", warning=FALSE}
library(ggplot2)
visalledu<-ggplot(mergedtest[mergedtest$Name=="FemaleOld" |mergedtest$Name=="FemaleMidAge"| mergedtest$Name=="FemaleYoung"| mergedtest$Name=="MaleOld" | mergedtest$Name=="MaleMidAge"| mergedtest$Name=="MaleYoung",],aes(Name,Success))
visalledu<-visalledu+geom_boxplot()
visalledu<-visalledu+labs(title ="Boxplot of estimated success probability",x="Category",y="Probability of Success")
print(visalledu)
#\caption{This box plot shows the probablity of success as estimated across males and females and different education levels}
#\label{boxsuccessalleducation}
#\end{figure}
```



\subsection{Funding}


```{r funding1, echo=FALSE,fig=TRUE, fig.width=7,fig.height=4, fig.cap="\\label{fig:boxfundingage}This box plot shows the probablity of funding as estimated across males and females and different age levels.",message=FALSE,warning=FALSE}
visalledu<-ggplot(mergedtest[mergedtest$Name=="FemaleOld" |mergedtest$Name=="FemaleMidAge"| mergedtest$Name=="FemaleYoung"| mergedtest$Name=="MaleOld" | mergedtest$Name=="MaleMidAge"| mergedtest$Name=="MaleYoung",],aes(Name,Funding))
visalledu<-visalledu+geom_boxplot()
visalledu<-visalledu+labs(title ="Boxplot of estimated funding probability",x="Category",y="Probability of Funding")
print(visalledu)
#\caption{This box plot shows the probablity of success as estimated across males and females and different education levels}
#\label{boxsuccessalleducation}
#\end{figure}
```



\subsection{Abandonment}

```{r abandon1, echo=FALSE,fig=TRUE, fig.width=7,fig.height=4, fig.cap="\\label{fig:boxabandonedu}This box plot shows the probablity of abandoning as estimated across males and females and different age levels.",message=FALSE,warning=FALSE}
visalledu<-ggplot(mergedtest[mergedtest$Name=="FemaleOld" |mergedtest$Name=="FemaleMidAge"| mergedtest$Name=="FemaleYoung"| mergedtest$Name=="MaleOld" | mergedtest$Name=="MaleMidAge"| mergedtest$Name=="MaleYoung",],aes(Name,Abandon))
visalledu<-visalledu+geom_boxplot()
visalledu<-visalledu+labs(title ="Boxplot of estimated abandoning probability",x="Category",y="Probability of Abandon")
print(visalledu)
#\caption{This box plot shows the probablity of abandoning as estimated across males and females and different education levels}
#\label{boxabandoningalleducation}
#\end{figure}
```



```{r multievaluatesignificantgender, results='asis', null_prefix=TRUE,echo=FALSE, warning=FALSE,error=FALSE,eval=FALSE}


GenderList<-c("Male", "Female") #as k and n
filelist<-c("FemaleYoung","FemaleMidAge","FemaleOld","MaleYoung","MaleMidAge","MaleOld")
 
parameter<-c("Success", "Funding", "Abandon") #as m
m<-1
for (i in 1:5){
   file1<-filter(mergedtest,mergedtest$Name==filelist[i])
      if(round(t.test(filter(file1,Gender=="Male")$Success,filter(file1,Gender=="Female")$Success)$p.value<0.1)){
   writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," as estimated by male and female respondents is " , round(t.test(filter(file1,Gender=="Male")$Success,filter(file1,Gender=="Female")$Success)$p.value,2),"."))
   }
 for (j in (i+1):6){
    file1<-filter(mergedtest,mergedtest$Name==filelist[i])
   file2<-filter(mergedtest,mergedtest$Name==filelist[j])
# 4 p value of file1$Success and file2$Success
if(round(t.test(file1$Success,file2$Success)$p.value,2)<0.1){
      writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j]," is " ,round(t.test(file1$Success,file2$Success)$p.value,2),".  "))
}
   

 }}

for (i in 1:5){
   file1<-filter(mergedtest,mergedtest$Name==filelist[i])
  for (j in (i+1):6){
    #for(k in 1:2){
      
       file2<-filter(mergedtest,mergedtest$Name==filelist[j])

if(round(t.test(filter(file1,Gender=="Male")$Success,filter(file2,Gender=="Male")$Success)$p.value,2) < 0.1){
       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Male respondents is " ,round(t.test(filter(file1,Gender=="Male")$Success,filter(file2,Gender=="Male")$Success)$p.value,2),"."))
}
  
if(round(t.test(filter(file1,Gender=="Female")$Success,filter(file2,Gender=="Female")$Success)$p.value,2) < 0.1){
     writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Female respondents is " ,round(t.test(filter(file1,Gender=="Female")$Success,filter(file2,Gender=="Female")$Success)$p.value,2),"."))
}       
   
 }}
###Funding
m<-2
for (i in 1:5){
   file1<-filter(mergedtest,mergedtest$Name==filelist[i])
  if(round(t.test(filter(file1,Gender=="Male")$Funding,filter(file1,Gender=="Female")$Funding)$p.value<0.1)){
   writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," as estimated by male and female respondents is " , round(t.test(filter(file1,Gender=="Male")$Funding,filter(file1,Gender=="Female")$Funding)$p.value,2),"."))
   }
 for (j in (i+1):6){
   
   file2<-filter(mergedtest,mergedtest$Name==filelist[j])
# 4 p value of file1$Funding and file2$Funding
if(round(t.test(file1$Funding,file2$Funding)$p.value,2)<0.1){
      writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j]," is " ,round(t.test(file1$Funding,file2$Funding)$p.value,2),".  "))
}
    
 }}

for (i in 1:5){
  for (j in (i+1):6){
    #for(k in 1:2){
       file1<-filter(mergedtest,mergedtest$Name==filelist[i])
       file2<-filter(mergedtest,mergedtest$Name==filelist[j])

if(round(t.test(filter(file1,Gender=="Male")$Funding,filter(file2,Gender=="Male")$Funding)$p.value,2) < 0.1){
       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Male respondents is " ,round(t.test(filter(file1,Gender=="Male")$Funding,filter(file2,Gender=="Male")$Funding)$p.value,2),"."))
}
  
if(round(t.test(filter(file1,Gender=="Female")$Funding,filter(file2,Gender=="Female")$Funding)$p.value,2) < 0.1){
     writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Female respondents is " ,round(t.test(filter(file1,Gender=="Female")$Funding,filter(file2,Gender=="Female")$Funding)$p.value,2),"."))
}       
   
 }}

###Abandon
m<-3

for (i in 1:5){
   file1<-filter(mergedtest,mergedtest$Name==filelist[i])
   if(round(t.test(filter(file1,Gender=="Male")$Abandon,filter(file1,Gender=="Female")$Abandon)$p.value<0.1)){
   writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," as estimated by male and female respondents is " , round(t.test(filter(file1,Gender=="Male")$Abandon,filter(file1,Gender=="Female")$Abandon)$p.value,2),"."))
   }
 for (j in (i+1):6){
   
   file2<-filter(mergedtest,mergedtest$Name==filelist[j])
# 4 p value of file1$Abandon and file2$Abandon
if(round(t.test(file1$Abandon,file2$Abandon)$p.value,2)<0.1){
      writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j]," is " ,round(t.test(file1$Abandon,file2$Abandon)$p.value,2),".  "))
}
   
  
 }}

for (i in 1:5){
  for (j in (i+1):6){
    #for(k in 1:2){
       file1<-filter(mergedtest,mergedtest$Name==filelist[i])
       file2<-filter(mergedtest,mergedtest$Name==filelist[j])

if(round(t.test(filter(file1,Gender=="Male")$Abandon,filter(file2,Gender=="Male")$Abandon)$p.value,2) < 0.1){
       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Male respondents is " ,round(t.test(filter(file1,Gender=="Male")$Abandon,filter(file2,Gender=="Male")$Abandon)$p.value,2),"."))
}
  
if(round(t.test(filter(file1,Gender=="Female")$Abandon,filter(file2,Gender=="Female")$Abandon)$p.value,2) < 0.1){
     writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Female respondents is " ,round(t.test(filter(file1,Gender=="Female")$Abandon,filter(file2,Gender=="Female")$Abandon)$p.value,2),"."))
}       
   
 }}

```


\subsection{Gender wise break up}
\subsubsection{Success}
```{r gendersuccess1, echo=FALSE,fig=TRUE, fig.width=7,fig.height=4, fig.cap="\\label{fig:boxgendersuccessage}This box plot shows the probablity of success as estimated by males and females across male and female founders with different education levels.",message=FALSE,warning=FALSE}
library(ggplot2)
visalledu<-ggplot(mergedtest[mergedtest$Name=="FemaleOld" |mergedtest$Name=="FemaleMidAge"| mergedtest$Name=="FemaleYoung"| mergedtest$Name=="MaleOld" | mergedtest$Name=="MaleMidAge"| mergedtest$Name=="MaleYoung",],aes(Name,Success))
visalledu<-visalledu+geom_boxplot(aes(colour = Gender))
visalledu<-visalledu+labs(title ="Boxplot of estimated success probability",x="Category",y="Probability of Success")
print(visalledu)
#\caption{This box plot shows the probablity of success as estimated across males and females and different education levels}
#\label{boxsuccessalleducation}
#\end{figure}
```


I compare how probability of success changes with the age of the founders changes with the gender of the respondents. 

```{r multievaluatesuccessgender, results='asis', null_prefix=TRUE,echo=FALSE, warning=FALSE,error=FALSE}

parameter<-c("Success", "Funding", "Abandon") #as m
m<-1
GenderList<-c("Male", "Female") #as k and n
filelist<-c("FemaleYoung","FemaleMidAge","FemaleOld","MaleYoung","MaleMidAge","MaleOld")
  for (i in 1:6){
        
        file1<-filter(mergedtest,mergedtest$Name==filelist[i])
 # 1 Mean of file1$Success # where file1 and file2 are as above
writeLines(paste0(" The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders is " ,round(mean(file1$Success,na.rm=TRUE),2),"."))

# 2 p value of file1$Success, filter(GenderList[i]) and file1$Success, filter(GenderList[j]) #Instead Male and Female. so IfElse not needed.
       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " estimated by male respondents and female respondents for startups founded by ",filelist[i]," is " , round(t.test(filter(file1,Gender=="Male")$Success,filter(file1,Gender=="Female")$Success)$p.value,2),"."))
       
       writeLines(paste0("The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders as per Malerespondents is " ,round(mean(filter(file1,Gender=="Male")$Success,na.rm=TRUE),2),".  "))
       
       writeLines(paste0("The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders as per Female respondents is " ,round(mean(filter(file1,Gender=="Female")$Success,na.rm=TRUE),2),".  "))
  }


for (i in 1:5){
 for (j in (i+1):6){
    file1<-filter(mergedtest,mergedtest$Name==filelist[i])
   file2<-filter(mergedtest,mergedtest$Name==filelist[j])
# 4 p value of file1$Success and file2$Success

      writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j]," is " ,round(t.test(file1$Success,file2$Success)$p.value,2),".  "))
 }}


for (i in 1:5){
  for (j in (i+1):6){
    #for(k in 1:2){
       file1<-filter(mergedtest,mergedtest$Name==filelist[i])
       file2<-filter(mergedtest,mergedtest$Name==filelist[j])

       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Male respondents is " ,round(t.test(filter(file1,Gender=="Male")$Success,filter(file2,Gender=="Male")$Success)$p.value,2),"."))
       
    writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Female respondents is " ,round(t.test(filter(file1,Gender=="Female")$Success,filter(file2,Gender=="Female")$Success)$p.value,2),"."))
 }}


```

SEE ABOVE THIS LINE.

\subsubsection{Funding}
```{r genderfunding1, echo=FALSE,fig=TRUE, fig.width=7,fig.height=4, fig.cap="\\label{fig:boxgenderfundingedu}This box plot shows the probablity of funding as estimated by males and females across male and female founders with different age levels.",message=FALSE,warning=FALSE}
visalledu<-ggplot(mergedtest[mergedtest$Name=="FemaleOld" |mergedtest$Name=="FemaleMidAge"| mergedtest$Name=="FemaleYoung"| mergedtest$Name=="MaleOld" | mergedtest$Name=="MaleMidAge"| mergedtest$Name=="MaleYoung",],aes(Name,Funding))
visalledu<-visalledu+geom_boxplot(aes(colour = Gender))
visalledu<-visalledu+labs(title ="Boxplot of estimated funding probability",x="Category",y="Probability of Funding")
print(visalledu)
#\caption{This box plot shows the probablity of success as estimated across males and females and different education levels}
#\label{boxsuccessalleducation}
#\end{figure}
```
As visible in Figure \@ref(fig:boxgenderfundingedu), the estimation of the funding of the startup also varies as per the gender of the respondent. 


```{r multievaluatefundinggender, results='asis', null_prefix=TRUE,echo=FALSE, warning=FALSE,error=FALSE}

parameter<-c("Success", "Funding", "Abandon") #as m
m<-2
GenderList<-c("Male", "Female") #as k and n
  filelist<-c("FemaleYoung","FemaleMidAge","FemaleOld","MaleYoung","MaleMidAge","MaleOld")
  for (i in 1:6){

        file1<-filter(mergedtest,mergedtest$Name==filelist[i])
 # 1 Mean of file1$Funding # where file1 and file2 are as above
writeLines(paste0(" The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders is " ,round(mean(file1$Funding,na.rm=TRUE),2),"."))

# 2 p value of file1$Funding, filter(GenderList[i]) and file1$Funding, filter(GenderList[j]) #Instead Male and Female. so IfElse not needed.
       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " estimated by male and female respondents for startups founded by ",filelist[i]," is " , round(t.test(filter(file1,Gender=="Male")$Funding,filter(file1,Gender=="Female")$Funding)$p.value,2),"."))
       
       writeLines(paste0("The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders as per Female respondents is " ,round(mean(filter(file1,Gender=="Female")$Funding,na.rm=TRUE),2),".  "))
       
       writeLines(paste0("The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders as per Male respondents is " ,round(mean(filter(file1,Gender=="Male")$Funding,na.rm=TRUE),2),".  "))
      
  }

for (i in 1:5){
 for (j in (i+1):6){
    file1<-filter(mergedtest,mergedtest$Name==filelist[i])
    file2<-filter(mergedtest,mergedtest$Name==filelist[j])
# 4 p value of file1$Funding and file2$Funding

      writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j]," is " ,round(t.test(file1$Funding,file2$Funding)$p.value,2),".  "))
 }}


for (i in 1:5){
  for (j in (i+1):6){
    #for(k in 1:2){
       file1<-filter(mergedtest,mergedtest$Name==filelist[i])
       file2<-filter(mergedtest,mergedtest$Name==filelist[j])
       
#       if(i == j) { ##Using Ifelse because WriteLines is an action.
#  0
#} else{
       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Male respondents is " ,round(t.test(filter(file1,Gender=="Male")$Funding,filter(file2,Gender=="Male")$Funding)$p.value,2),"."))
       
       
    writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Female respondents is " ,round(t.test(filter(file1,Gender=="Female")$Funding,filter(file2,Gender=="Female")$Funding)$p.value,2),"."))
#}
 }}

```



\subsubsection{Abandon}
```{r genderabandon1, echo=FALSE,fig=TRUE, fig.width=7,fig.height=4, fig.cap="\\label{fig:boxgenderabandonedu}This box plot shows the probablity of abandoning as estimated by males and females across male and female founders with different education levels.",message=FALSE,warning=FALSE}
visalledu<-ggplot(mergedtest[mergedtest$Name=="FemaleOld" |mergedtest$Name=="FemaleMidAge"| mergedtest$Name=="FemaleYoung"| mergedtest$Name=="MaleOld" | mergedtest$Name=="MaleMidAge"| mergedtest$Name=="MaleYoung",],aes(Name,Abandon))
visalledu<-visalledu+geom_boxplot(aes(colour = Gender))
visalledu<-visalledu+labs(title ="Boxplot of estimated abandoning probability.",x="Category",y="Probability of Abandon")
print(visalledu)
#\caption{This box plot shows the probablity of abandoning as estimated across males and females and different education levels}
#\label{boxabandoningalleducation}
#\end{figure}
```

As visible in Figure \@ref(fig:boxgenderabandonedu), the estimation of the abandoning of the startup also varies as per the gender of the respondent. 


```{r multievaluateabandongender, results='asis', null_prefix=TRUE,echo=FALSE, warning=FALSE,error=FALSE}

parameter<-c("Success", "Funding", "Abandon") #as m
m<-3
GenderList<-c("Male", "Female") #as k and n
  filelist<-c("FemaleYoung","FemaleMidAge","FemaleOld","MaleYoung","MaleMidAge","MaleOld")
  for (i in 1:6){

        file1<-filter(mergedtest,mergedtest$Name==filelist[i])
        
 # 1 Mean of file1$Funding # where file1 and file2 are as above
writeLines(paste0(" The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders is " ,round(mean(file1$Abandon,na.rm=TRUE),2),"."))

# 2 p value of file1$Abandon, filter(GenderList[i]) and file1$Abandon, filter(GenderList[j]) #Instead Male and Female. so IfElse not needed.
       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," as estimated by male and female respondents is " , round(t.test(filter(file1,Gender=="Male")$Abandon,filter(file1,Gender=="Female")$Abandon)$p.value,2),"."))
  writeLines(paste0("The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders as per male respondents is " ,round(mean(filter(file1,Gender=="Male")$Abandon,na.rm=TRUE),2),".  "))
  writeLines(paste0("The mean estimate of ",parameter[m], " of a startup founded by ", filelist[i], " founders as per female respondents is " ,round(mean(filter(file1,Gender=="Female")$Abandon,na.rm=TRUE),2),".  "))
       
       }

for (i in 1:5){
 for (j in (i+1):6){
   file1<-filter(mergedtest,mergedtest$Name==filelist[i])
   file2<-filter(mergedtest,mergedtest$Name==filelist[j])

      writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j]," is " ,round(t.test(file1$Abandon,file2$Abandon)$p.value,2),".  "))
 }}


for (i in 1:5){
  for (j in (i+1):6){
    #for(k in 1:2){
       file1<-filter(mergedtest,mergedtest$Name==filelist[i])
       file2<-filter(mergedtest,mergedtest$Name==filelist[j])

       writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Male respondents is " ,round(t.test(filter(file1,Gender=="Male")$Abandon,filter(file2,Gender=="Male")$Abandon)$p.value,2),"."))
    writeLines(paste0( "The p-value of the difference between estimated probability of ",parameter[m], " for startups founded by ",filelist[i]," and ",filelist[j], " as estimated by Female respondents is " ,round(t.test(filter(file1,Gender=="Female")$Abandon,filter(file2,Gender=="Female")$Abandon)$p.value,2),"."))
 }}


```


\section{Conclusion}

The p-value of the difference between estimated probability of Success for startups founded by FemaleMidAge and MaleYoung is 0.08.
The p-value of the difference between estimated probability of Success for startups founded by FemaleYoung and FemaleMidAge as estimated by Female respondents is 0.04.
The p-value of the difference between estimated probability of Success for startups founded by FemaleMidAge and MaleYoung as estimated by Female respondents is 0.08.

The p-value of the difference between estimated probability of Funding for startups founded by FemaleMidAge as estimated by male and female respondents is 0.02.
The p-value of the difference between estimated probability of Funding for startups founded by FemaleYoung and FemaleMidAge as estimated by Female respondents is 0.01.
The p-value of the difference between estimated probability of Funding for startups founded by FemaleYoung and MaleOld as estimated by Male respondents is 0.09.
The p-value of the difference between estimated probability of Funding for startups founded by FemaleMidAge and MaleMidAge as estimated by Male respondents is 0.09.
The p-value of the difference between estimated probability of Funding for startups founded by FemaleMidAge and MaleOld as estimated by Male respondents is 0.02.
The p-value of the difference between estimated probability of Funding for startups founded by FemaleMidAge and MaleOld as estimated by Female respondents is 0.02.
The p-value of the difference between estimated probability of Funding for startups founded by FemaleOld and MaleOld as estimated by Male respondents is 0.06.

The p-value of the difference between estimated probability of Abandon for startups founded by FemaleOld and MaleYoung is 0.04. 
The p-value of the difference between estimated probability of Abandon for startups founded by FemaleMidAge and FemaleOld as estimated by Male respondents is 0.06.
The p-value of the difference between estimated probability of Abandon for startups founded by FemaleOld and MaleYoung as estimated by Male respondents is 0.04.
The p-value of the difference between estimated probability of Abandon for startups founded by FemaleOld and MaleMidAge as estimated by Male respondents is 0.06.

Younger males are more likely to success than MidAge females. Surprisingly females are driving this. It could be because 31,32 is the age for going the family way. This is evident in the fact that they rate 21,22 year old female founders as more likely to succeed, even more than YoungMale.

Consistently females have estimated the probability of funding for a startup founded by 31,32 year old females as much lower than that estimated by male respondents. Funding is a measure of how respondents feel investors would perceive the startup/founders. This means female respondents feel that investors would also not value 31,32 year old female founders, as opposed to male respondents. The estimate of female respondents for a startup founded by 21,22 year old females is higher than that of a startup founded by 31,32 year old females.

Male respondents felt that the probability of funding for a startup founded by young females was higher than that founded by older males. Surprisingly males also felt the probability of funding for a startup founded by 32,33 year old female founders was higher than that of a startup founded by 32,33 year old males. Their estimate for funding probability for older males was lower than that of 32,33 year old female founders also. On the contrary, female respondents felt that the probability of 42,43 year old males getting funded for their startup was higher than that of a startup founded by 32,33 year old females.

22,23 year old males were more likely to abandon their startup than 42,43 year old females. Males estimated that 32,33 year old females were more likely to abandon their startup as compared to 42,43 year old female founders who were also less likely than 22,23 year old males to abandon theirs. Surprisingly male respondents felt that 32,33 year old males were more likely than 32,33 year old females to abandon their startup.



\subsection{Older}


We see a clear difference between the estimated probability of success for startups driven by young female founders versus those driven by old female founders. The difference is driven more by female respondents. We also see that there is no statistically significant difference in the estimated probability of abandoning the startup between older males and female founders. There is a difference in the estimated probability of abandoning the startup in case of young male founders. This is also driven by female respondents.

1. Female founders= Education plays a role more, than in the case of males. This is also driven by female respondents. This means if a product is targeted towards
2. Abandoning is not a problem in the case of females, as was being expected earlier. Good signal, social change.
3. Abandoning by young males was considered a risk, especially by female respondents. This means a B2C product focused on women, sold by a startup founded by young males, is less likely to work if it involves a longevity assumption on the part of the customer. Similarly in case of a B2B product, if the person on the buyer's side is a female, the startup founders should invest in signalling longevity, stability and their intent to stay along with a plan to sustain.


We see that while there is no difference in the perception of success, funding or abandonment of a startup based on whether the founders are CASE 1 or CASE 2, we see that the perception of males and females varies. 
A practical import of this would be
* If the product is targeted towards females, Vs males
* If the investor who is evaluating the startup for funding is a male Vs Female
* (IN case of abandon), then the founders should spend time showing commitment
* This could explain some difference between the funding obtained by women

\section{Limitations}
* Situation is dynamic
* Investors might be more sophisticated and not be biased though extant research has shown otherwise \footnote{ADD Literature}

###########Older Material ###############


	\section{Limitations}
		We do not analyse the results based on the background of the respondents. We take only discrete age variables. These can be extended to 52,53 and 62, 63 as well. 
		We do not look at Foreign education.
		We do not specify the role in government service. It is possible that a bureaucrat is respected much more than any other civil servant.
		
\section{ToDO}
*   Correct Labels
*   Write as per plan of View followed by Gender
*   Write a separate one on familiarity.

